Characterizing Execution Times on Realistic Programs

### 2018-05-01 pt_characterization/real_data/paper.tex
New drafts

\section{Preliminary Experiments}

\subsection{Inter-machine Repeatability Check~\label{sec:diff_machine}}

In this section we check if the use of different machines affects the distribution of execution (process) times on the same program. 
In other words, we examine {\em inter-machine repeatability}. For this examination, we use a nested for loop program, here termed INC, 
with different task lengths: 16 seconds, 13 seconds, and 17.2 seconds, each termed {\em INC16}, {\em INC13}, and {\em INC17.2}, respectively.

Figures~\ref{fig:dm_1}, ~\ref{fig:dm_2}, and ~\ref{fig:dm_3} display the process time (PT) histograms on INC16, INC13, and INC17.2 run on our machines (from {\tt sodb8} to {\tt sodb12}), respectively. Based on these figures, we conclude that we should stick to one machine  for consistency, and {\tt sodb9} should be chosen in a sense that the data measured there consistently reveals a distinct binormal pattern.

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on INC16]{
		\includegraphics[scale=0.43]{sodb8_INC16_0_dist.eps}
		\label{fig:s8_inc16_dist}
	}	
	\subfigure[PT frequency on INC16]{
		\includegraphics[scale=0.43]{sodb9_INC16_0_dist.eps}
		\label{fig:s9_inc16_dist}
	}
	\subfigure[PT frequency on INC16]{
		\includegraphics[scale=0.43]{sodb10_INC16_0_dist.eps}
		\label{fig:s10_inc16_dist}
	}	
	\subfigure[PT frequency on INC16]{
		\includegraphics[scale=0.43]{sodb12_INC16_0_dist.eps}
		\label{fig:s12_inc16_dist}
	}
	\caption{PT Histograms on INC16~\label{fig:dm_1}}
\end{figure}

\newpage
\clearpage

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on INC13]{
		\includegraphics[scale=0.43]{sodb8_INC13_0_dist.eps}
		\label{fig:s8_inc13_dist}
	}	
	\subfigure[PT frequency on INC13]{
		\includegraphics[scale=0.43]{sodb9_INC13_0_dist.eps}
		\label{fig:s9_inc13_dist}
	}
	\subfigure[PT frequency on INC13]{
		\includegraphics[scale=0.43]{sodb10_INC13_0_dist.eps}
		\label{fig:s10_inc13_dist}
	}	
	\subfigure[PT frequency on INC13]{
		\includegraphics[scale=0.43]{sodb12_INC13_0_dist.eps}
		\label{fig:s12_inc13_dist}
	}
	\caption{PT Histograms on INC13~\label{fig:dm_2}}
\end{figure}

\newpage
\clearpage

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on INC17.2]{
		\includegraphics[scale=0.43]{sodb8_INC17_2_dist.eps}
		\label{fig:s8_inc17_2_dist}
	}	
	\subfigure[PT frequency on INC17.2]{
		\includegraphics[scale=0.43]{sodb9_INC17_2_dist.eps}
		\label{fig:s9_inc17_2_dist}
	}
	\subfigure[PT frequency on INC17.2]{
		\includegraphics[scale=0.43]{sodb10_INC17_2_dist.eps}
		\label{fig:s10_inc17_2_dist}
	}	
	\subfigure[PT frequency on INC17.2]{
		\includegraphics[scale=0.43]{sodb12_INC17_2_dist.eps}
		\label{fig:s12_inc17_2_dist}
	}
	\caption{PT Histograms on INC17.2~\label{fig:dm_3}}
\end{figure}

\newpage
\clearpage

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on SORT144 on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sort244_dist.eps}
		\label{fig:sort144_dist}
	}	
	\subfigure[PT frequency on INC25.8 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{inc25.8_dist.eps}
		\label{fig:inc25.8_dist}
	}
	\subfigure[PT frequency on SORT288  on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sort177_dist.eps}
		\label{fig:sort177_dist}
	}	
	\subfigure[PT frequency on INC35 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{inc13.0_dist.eps}
		\label{fig:inc35_dist}
	}
	\caption{PT Histogram Comparison II~\label{fig:sort2}}
\end{figure}

@@

>>>>

@@

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on SORT244 on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sort244_dist.eps}
		\label{fig:sort244_dist}
	}	
	\subfigure[PT frequency on INC25.8 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{inc25.8_dist.eps}
		\label{fig:inc25.8_dist}
	}
	\subfigure[PT frequency on SORT288  on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sort288_dist.eps}
		\label{fig:sort288_dist}
	}	
	\subfigure[PT frequency on INC35 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{inc35.0_dist.eps}
		\label{fig:inc35_dist}
	}
	\caption{PT Histogram Comparison II~\label{fig:sort2}}
\end{figure}
